% titanic-5-minutes.tex
\documentclass{screenplay}

\title{Titanic\\The 8-minute musical}
\author{Anonymous}
\address{Bremerton Community Theatre\\WA

April 5th to May 5th

2024
}

\newcommand{\andrews}[1]{\begin{dialogue}{Andrews}#1\end{dialogue}}
\newcommand{\alice}[1]{\begin{dialogue}{Alice}#1\end{dialogue}}
\newcommand{\barrett}[1]{\begin{dialogue}{Barrett}#1\end{dialogue}}
\newcommand{\bellboy}[1]{\begin{dialogue}{Bellboy}#1\end{dialogue}}
\newcommand{\bride}[1]{\begin{dialogue}{Bride}#1\end{dialogue}}
\newcommand{\captain}[1]{\begin{dialogue}{Captain}#1\end{dialogue}}
\newcommand{\caroline}[1]{\begin{dialogue}{Caroline}#1\end{dialogue}}
\newcommand{\charles}[1]{\begin{dialogue}{Charles}#1\end{dialogue}}
\newcommand{\edgar}[1]{\begin{dialogue}{Edgar}#1\end{dialogue}}
\newcommand{\etches}[1]{\begin{dialogue}{Etches}#1\end{dialogue}}
\newcommand{\farrell}[1]{\begin{dialogue}{Farrell}#1\end{dialogue}}
\newcommand{\hartley}[1]{\begin{dialogue}{Hartley}#1\end{dialogue}}
\newcommand{\ismay}[1]{\begin{dialogue}{Ismay}#1\end{dialogue}}
\newcommand{\kate}[1]{\begin{dialogue}{Kate}#1\end{dialogue}}
\newcommand{\lightoller}[1]{\begin{dialogue}{Lightoller}#1\end{dialogue}}
\newcommand{\murdoch}[1]{\begin{dialogue}{Murdoch}#1\end{dialogue}}
\newcommand{\strauss}[1]{\begin{dialogue}{Strauss}#1\end{dialogue}}
\newcommand{\officer}[1]{\begin{dialogue}{Officer}#1\end{dialogue}}
\newcommand{\third}[1]{\begin{dialogue}{Third class passengers}#1\end{dialogue}}
\newcommand{\second}[1]{\begin{dialogue}{Second class passengers}#1\end{dialogue}}
\newcommand{\first}[1]{\begin{dialogue}{First class passengers}#1\end{dialogue}}
\newcommand{\company}[1]{\begin{dialogue}{Company}#1\end{dialogue}}

\begin{document}
\coverpage
\fadein

\intslug{Titanic set}

Overture (reversed Jaws theme)

1a

Enter ANDREWS, BARRET.

\andrews{
    Sleek and fast.
    Screaming one man's exstacy.
}

2

\barrett{
    How did they build Titanic?
    46,000 tons of meat, poultry and fish!
}

2a

Enter BRIDE.

\barrett{
    Fare thee well, Mr Bride, chief taster at the
    Macaroni International Pasta and Marinara Sauce Cooking Company, Limited.
}

2b

Enter OFFICERS, CAPTAIN.

\officer{
    Ship of dreams!  Morning everyone!
}

\andrews{
    One old town motorcar, with steamy windows.  Titanic!
}

\captain{
    Size and speed? Uninsured!
}

2d

\ismay{
    Dominion over the world!
}

Ismay twirls his moustache.

\ismay{
    The fastest ship for the mail.
    The largest moving object.
    Bring on the passengers!
}

2e

\officer{
    Third class passengers, get your butts up the gangway!
}

\third{
    You'd need a golf cart to get to the front, Kate.
    Are you Irish, Kate?
    I will be, when I marry him!
}

2g

\officer{
    Second class passengers, go and arrange your dinner!
}

\second{
    Let's run away and marry!
    They're so sensible over there, and we're almost American!
}

\officer{
    First class passengers, welcome aboard!
}

2h

\first{
    Astor, Strass, Gugenheim, Widener, Thayer, Cardoza and Peggy.
}

2j

\officer{
    Jetway lowered, Captain!
}

\company{
    Farewell Titanic!
    Sing Godspeed to thee,
    With no foreboding.
}

\intslug{Bridge.}

3

\officer{
    We've cleared Wolf Rock.
}

\company{
    Howl!
}

\officer{
    There's no moon, guys!
}

\ismay{
    I brought celebratory libations!
}

\captain{
    I don't allow alcohol on my bridge, without ice.
    We must find some ice: 19 knots!
}

\intslug{Boiler room.}

6

\barrett{
    What are the boys from the Midlands doing?
    We're the Thunder from Down Under Deck, and really hot!
    Turn the screws faster!
}

\intslug{Second class deck.}

7

\alice{
    How impressed they'll all be,
    when they hear,
    all that you know about polar bears.
}

7a

\caroline{
    We're like a married couple.
}

\charles{
    Sarcasm's already started.
}

\intslug{First class dining room.}

8

\etches{
    My dear Mr Latimer!
}

\first{
    What a remarkable serving staff!
    What a remarkable dinner!
    What a remarkable conversation about navigation statistics!
}

\captain{
    What an remarkable iceberg.  Where's my gin and tonic?  Bye ladies!
}

\bellboy{
    Go to the caf\'e... there will be cake!
}

\intslug{Bridge.}

9

\captain{
    What are the sea temperatures?
}

\officer{
    Have you ever used a veterinary rectal thermometer?
}

\captain{
    We'll keep a sharp eye for polar bears---ever onward!
}

10

\murdoch{
    Thousands on board,
    I have a bad feeling about this.
}

\intslug{Third class dining room.}

11

\etches{
    Third class passengers are reminded to carry their rats in an approved container.
}

\third{
    I will be a proper person,
    In America, F*ck Yeah!
}

Applause.  USA!  USA!  USA!

\extslug{Second class deck.}

\etches{
    Why Lady Caroline, perhaps I can offer your husband a more expensive wig?
}

12

Charles is indignant.

\charles{
    I have all that I want!
}

\caroline{
    Charles, it is such a silly thing.
}

\intslug{Bridge.}

13

\officer{
    It's bloody cold.  Polar bears are afraid.
}

\ismay{
    It's a new world, Andrews.  People want speed.
}

\andrews{
    Then, later on, we can place the blame on market economics.
}

\intslug{Radio/pasta room.}

15

\barrett{
    I want to send an, ahem, romantic message to England.
}

\bride{
    We charge extra for sexting.
}

\barrett{
    What if I sing a song about it?
}

\bride{
    Then the royalties will cover the expense!
    How do you spell Darlene?
}

\barrett{
    Make sure you sign it Fred, now.
}

Dit, dit, dah, dit, ahh.

\extslug{Disco deck.}

16

\captain{
    Let us sing hymn number 27, God Bring Me Ice.
}

\company{
    Isn't it a lovely day to rag with new friends.
    Everyone is bursting with emotion,
    trying to remember which foot is next.
}

\intslug{Second class corridor.}

17a

Enter EDGAR, exasperated.

\edgar{
    Oh HARDWARE!
}

\alice{
    Applesauce, Edgar.
}

\intslug{Bridge.}

\captain{
    Mr Murdoch, what's our present speed?
}

\murdoch{
    Forgotten, sir.
}

\captain{
    Have there been ANY reports of speed?
}

\murdoch{
    None at all sir.
}

\captain{
    Increase speed by... two then.
}

\officer{
    Reports of an iceberg ahead, sir.
}

\captain{
    Thank God I won't see it.
}

\extslug{Deck.}

18a

\etches{
    I had a wife once.
}

\edgar{
    My condolences.
}

\farrell{
    Kate, do you know who the father is?
}

\kate{
    Someone who forgot the check his fly, boyo!
}

\intslug{Bridge.}

\captain{
    The weather's quite changed, Mr. Lightoller.
}

\lightoller{
    Yes, sir, it's turned very cold.
    Polar bears are sitting straight up.
}

\captain{
    Keep your eyes peeled for ice.  My bedtime Martini is tepid.
}

\extslug{Deck.}

\caroline{
    What's the first thing you'll do when we reach America, darling?
}

\charles{
    Find a wig with a good deal more padding.
}

\intslug{Fist class dining saloon.}

\hartley{
    Awesome!

    My costume change is so awesome!

    Playing more cowbell is awesome!

    It's a new world over there!
}

\extslug{Deck.}

\company{
    No moon.  No wind.  No wave.
    No swell.  No binoculars.
    Iceberg!
}

End of act 1.

\intslug{Bridge.}

22

\captain{
    Wake up the passengers.  They could use a drill.
}

\andrews{
    Not til strike, sir.
}

\captain{
    Close the water-tight doors!
    Our position, Mr Murdock?
}

\murdoch{
    I'm not sure, sir.
}

\captain{
    Then I declare this ship lost!
}

\intslug{Indeterminate magic dining room.}

\caroline{
    I need to finish my book.
}

\alice{
    I need to finish my face.
}

\intslug{Bridge.}

\captain{
    I need to finish my Martini.
}

\ismay{
    EJ, why have we stopped?
}

\captain{
    We needed to collect some ice from the deck.
}

\ismay{
    God Himself could finish your drink.
}

\captain{
    How long have I got?
}

\andrews{
    Two hours at the most.
}

\captain{
    Cheers then!
}

\intslug{First class grand salon.}

23

\first{
    Strange and quite disorienting being here.

    These pajamas cost \pounds 500!

    But the life vests, I am guessing,
    
    Dug from the ground.
}

\intslug{Third class dungeon.}

\kate{
    Are we swimming to America?
}

\barrett{
    God will decide that the 1st class get the lifeboats.
}

\kate{
    But what about the Californian?
}

\barrett{
    They're too cool for lifeboats.
}

\intslug{Bridge.}

24

\captain{
    You did it!
}

\andrews{
    You did it!
}

ISMAY twirls moustache.

\ismay{
    I did it.  And you can't handle the truth!
}

\extslug{Boat deck.}

\etches{
    Women and children into the lifeboats!
}

\murdoch{
    Everyone into the lifeboats.
    Not you.

    Can you row?
}

\farrell{
    I can now!  I'm a fisherman, dammit, not a constable!
}

26

\company{
    We'll meet tomorrow, and every weekend for a month.
}

\edgar{
    That water looks colder than a polar bear's keester.
}

\company{
    What's with the polar bears?
}

\intslug{Bridge.}

\captain{
    I've been uncommonly lucky. Only one hull breech, and two groundings.
    Which are not calamaties worth speaking of.
    But now this, and only two days until retirement.
}

\extslug{Deck.}

\strauss{
    Still, a shame to break one of the 20,000 plastic drinking glasses.
    Still.
    Still?
}

\intslug{Andrews' room.}

30

\bellboy{
    Mr Andrews, are you going to make a go of it?
}

\andrews{
    The bulkheads are too low.

    Awful.

    This has not been quite so awesome.
}

\extslug{Carpathia.}

\etches{
    One moment the ship was there.
}

\kate{
    And my husband.
    And my husband.
    Then they totally disappeared.
}

\company{
    Fare thee well.

    China's wall.  Stonehenge.  Parthenon.  Pyramids, mammoths, and polar bears.
    
    Our task was to create a floating city.

    Sail on, Titanic!
    Godspeed to thee!
}

\theend
\end{document}
